\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[a4paper,landscape,margin=1.45cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!55!black,
  urlcolor=blue!55!black
}

\newcommand{\coef}[2]{#1; $p=#2$}
\newcommand{\sig}{$p<0.001$}
\newcommand{\mc}[1]{\multicolumn{1}{c}{#1}}

\title{Platform Membership and Marketing-Mix Effectiveness\\
\large Formal Feature Definitions, Model Tests, Results, and Interpretation}
\author{JAMS Platform Membership Analysis}
\date{\today}

\begin{document}
\maketitle

\section{Research Objective}

The empirical question is whether membership in a mobility platform changes how
marketing-mix instruments translate into provider performance. The theoretical point is
not that platforms should mechanically increase utilisation. A platform can create demand,
but it can also intensify comparison, increase price salience, and expose weak elements of
the provider's offer. The analysis therefore treats platform membership as a market-interface
condition that can moderate the effect of price, promotion, place, product, and process
features.

The empirical setting is a city--provider--day panel from March 11, 2024 to August 22,
2024. The main analysis uses 14,514 observations from 97 city--provider units across 30
cities. The primary outcome is transformed capacity utilisation. For selected robustness
tests, we also use transformed trip activity as a secondary outcome. Platform membership is
defined as substantive bookable/payable integration in a platform interface; weaker forms
of exposure such as pure routing information or visibility are treated separately.

\section{Notation}

Let $i$ index providers, $c$ cities, $t$ calendar days, and $m(i)$ the provider's mobility
mode. The outcome is $Y_{ict}$, transformed capacity utilisation for provider $i$ in city
$c$ on day $t$. The secondary outcome is $Q_{ict}$, transformed trip activity.

Platform membership is denoted by $P_{ict}$. We distinguish three mutually informative
platform architectures:
\[
P^{A}_{ict}=\text{large aggregator only}, \quad
P^{L}_{ict}=\text{local MaaS only}, \quad
P^{M}_{ict}=\text{multi-platform membership}.
\]
The omitted comparison group consists of provider--city--days without clean bookable/payable
platform membership.

Marketing-mix variables are grouped as follows:
\[
\mathcal{M}_{ict}=\{U_{ict}, R_{ict}, H_{ict}, B_{ict}, V_{ict}, C_{ict}, E_{ict}, A_{ict}, N_{ict}\}.
\]
Here, $U_{ict}$ is the unlock fee, $R_{ict}$ is the per-minute price, $H_{ict}$ is promotion
activity, $B_{ict}$ is product breadth, $V_{ict}$ is relative active-vehicle availability,
$C_{ict}$ is direct same-mode competition, $E_{ict}$ is same-platform competition, $A_{ict}$
captures commute-oriented usage, and $N_{ict}$ captures night-oriented usage.

All continuous moderator variables used in interactions are standardised before estimation,
except for binary threshold and promotion indicators. Standardisation makes interaction
coefficients comparable across feature families.

\section{Feature Definitions}

\subsection{Platform Architecture}

Clean platform membership equals one when a provider can be substantially accessed through
the platform interface. The coding requires bookable/payable integration or comparable
substantive transaction integration. Weak visibility, route information, or unclear exposure
is not treated as full membership. Platform architecture is then split into large aggregator
membership, local public MaaS membership, and simultaneous membership in both types.

\subsection{Pricing Features}

The absolute unlock-fee threshold feature is
\[
D^{\tau}_{ict}=\mathbb{1}\{U_{ict}\geq \tau\},
\]
where $\tau$ is a salient threshold such as EUR 1.00 or EUR 1.20. This feature captures
whether the provider charges an upfront access fee high enough to become salient before
the ride begins.

The relative same-mode unlock-fee disadvantage is defined as
\[
\Delta^{U}_{ict}=z\left(U_{ict}-\min_{j\in \mathcal{S}_{ct}(m(i))} U_{jct}\right),
\]
where $\mathcal{S}_{ct}(m(i))$ is the set of providers in city $c$ on day $t$ that operate
in the same mobility mode as provider $i$, and $z(\cdot)$ denotes standardisation. If a
provider is the cheapest same-mode option, the raw gap is zero. This feature operationalises
relative access-price disadvantage: the provider is not merely expensive in absolute terms,
but expensive relative to directly comparable alternatives.

Analogously, the relative per-minute price disadvantage is
\[
\Delta^{R}_{ict}=z\left(R_{ict}-\min_{j\in \mathcal{S}_{ct}(m(i))} R_{jct}\right).
\]
This parallel feature allows us to test whether platform membership amplifies all price
differences or specifically upfront price salience.

\subsection{Competition and Availability}

Direct same-mode competition is measured as
\[
C_{ict}=\left|\mathcal{S}_{ct}(m(i))\right|-1,
\]
standardised for modelling. It counts how many directly comparable same-mode alternatives
are active in the same city on the same day.

Same-mode active-vehicle share is
\[
V_{ict}=\frac{Fleet_{ict}}{\sum_{j\in \mathcal{S}_{ct}(m(i))} Fleet_{jct}},
\]
where $Fleet_{ict}$ is the active vehicle count for provider $i$ in city $c$ on day $t$.
This captures the provider's relative availability position among direct substitutes.

Same-platform competition counts providers that are visible or bookable through the same
platform environment. This feature is theoretically important because platforms can create
within-interface comparison. Empirically, however, it is tightly linked to platform
architecture and city/provider structure, so it is treated cautiously.

\subsection{Product, Promotion, and Process Features}

Product breadth, $B_{ict}$, is the standardised number of vehicle types offered by the
provider in the city--day. The interpretation is straightforward: broader assortment can
increase modal fit and may buffer pricing frictions.

Promotion activity, $H_{ict}$, captures whether a provider--city--day is covered by an
identified promotion. We distinguish broad promotion activity from more specific usage-cost
reducing promotions, such as free minutes for public-transport subscribers. These specific
promotions are theoretically relevant because they reduce marginal usage cost or offset
access-price salience, but their current empirical support is localized.

Commute-oriented usage and night-oriented usage are derived from the distribution of observed
trips over the day. The night-share feature, $N_{ict}$, captures whether provider usage is
disproportionately concentrated in evening and night contexts. This is a process/context
feature: it indicates the kind of usage situation in which the service is being consumed.

Provider-level product/process affordances include reservation availability, pass/free-unlock
availability, minute-bundle availability, and parking/geofence rules. These are useful for
describing the marketing mix, but current variation is mostly provider-level rather than
city--date specific. They are therefore treated as theory-supporting features unless future
data provide historical city-level timing.

\section{Model Specification}

We estimate fixed-effect models with cluster-robust standard errors at the city--provider
level. Two fixed-effect structures are used throughout:
\[
\alpha^{M}_{ict}=\lambda_c+\mu_i+\delta_t
\]
for market fixed effects, and
\[
\alpha^{U}_{ict}=\psi_{ic}+\delta_t
\]
for unit fixed effects. The market specification controls for city, provider, and day
differences. The unit specification is stricter because it identifies within city--provider
variation over time, net of day shocks.

\subsection{Platform Main Effect}

The baseline platform model is
\[
Y_{ict}=\beta P_{ict}+X_{ict}'\Gamma+\alpha_{ict}+\varepsilon_{ict}.
\]
This model asks whether platform membership is associated with a uniform utilisation shift.
It is intentionally not the central theory test; it is a diagnostic benchmark.

\subsection{Marketing-Mix Moderation}

The general moderation model is
\[
Y_{ict}=\beta_1 M_{ict}+\beta_2 P_{ict}
\beta_3(M_{ict}\times P_{ict})+X_{ict}'\Gamma+\alpha_{ict}+\varepsilon_{ict}.
\]
The coefficient $\beta_3$ tests whether platform membership changes the effectiveness of a
marketing-mix feature $M_{ict}$.

\subsection{Platform-Architecture Moderation}

For platform types, we estimate
\[
Y_{ict}=\sum_{k\in\{A,L,M\}}\theta_k(M_{ict}\times P^{k}_{ict})
 +X_{ict}'\Gamma+\alpha_{ict}+\varepsilon_{ict}.
\]
The key terms are $\theta_L$ and $\theta_M$, because the theory predicts stronger comparison
effects in local MaaS and multi-platform contexts than in large aggregator-only contexts.

\subsection{High Unlock-Fee Threshold Models}

The threshold model is
\[
Y_{ict}=\sum_{k\in\{A,L,M\}}\gamma_{k\tau}(D^{\tau}_{ict}\times P^{k}_{ict})
+X_{ict}'\Gamma+\alpha_{ict}+\varepsilon_{ict}.
\]
Here $\gamma_{k\tau}$ tests whether a salient upfront fee threshold is especially harmful
inside platform architecture $k$.

\subsection{Relative Price-Position Models}

The relative price-position model is
\[
Y_{ict}=\sum_{k\in\{A,L,M\}}\eta_k(\Delta^U_{ict}\times P^{k}_{ict})
+X_{ict}'\Gamma+\alpha_{ict}+\varepsilon_{ict}.
\]
This is the cleanest empirical test of the comparison-salience mechanism: if platforms make
direct alternatives more comparable, then being more expensive than same-mode competitors
should be particularly harmful in platform contexts.

\subsection{Product-Buffer Model}

To test whether product breadth buffers pricing friction, we estimate
\[
Y_{ict}=\sum_{k\in\{A,L,M\}}\rho_k(D^{1.00}_{ict}\times P^{k}_{ict}\times B_{ict})
+X_{ict}'\Gamma+\alpha_{ict}+\varepsilon_{ict}.
\]
A positive $\rho_L$ means that product breadth weakens the Local MaaS high-fee penalty.

\section{Results}

\setlength{\tabcolsep}{2.8pt}
\renewcommand{\arraystretch}{1.18}
\small
\begin{longtable}{p{0.075\linewidth}p{0.245\linewidth}p{0.115\linewidth}p{0.13\linewidth}p{0.13\linewidth}p{0.235\linewidth}}
\caption{Relevant Empirical Findings}\\
\toprule
\textbf{Finding} & \textbf{Substantive result} & \textbf{Robustness} &
\textbf{Market fixed effects} & \textbf{Unit fixed effects} & \textbf{Empirical basis}\\
\midrule
\endfirsthead
\toprule
\textbf{Finding} & \textbf{Substantive result} & \textbf{Robustness} &
\textbf{Market fixed effects} & \textbf{Unit fixed effects} & \textbf{Empirical basis}\\
\midrule
\endhead
\bottomrule
\endfoot

F1 & Platform membership does not create a stable generic utilisation lift. &
Not robust as a main effect &
\coef{0.061}{0.008} &
\coef{-0.010}{0.205} &
Full sample, $N=14{,}514$. The positive association disappears in the stricter within-unit model. \\

F2 & Unlock fees become more detrimental in platform contexts. &
Robust in market models; weaker within-unit &
\coef{-0.0715}{<0.001} &
\coef{-0.0236}{0.349} &
Full sample, $N=14{,}514$. Repeated negative evidence across concept and pricing models. \\

F3 & High unlock fees are harmful in platform contexts. &
Robust &
\coef{-0.104}{<0.001} &
\coef{-0.040}{<0.001} &
Full sample, $N=14{,}514$. Negative in all six threshold specifications. \\

F3/F4 & High unlock fees are especially harmful in Local MaaS contexts. &
Very robust &
\coef{-0.150}{0.002} &
\coef{-0.046}{<0.001} &
Full sample, $N=14{,}514$. Stable across threshold and platform-type model families. \\

F3/F4 & High unlock fees are especially harmful in multi-platform contexts. &
Very robust &
\coef{-0.131}{0.007} &
\coef{-0.098}{<0.001} &
Full sample, $N=14{,}514$. Stable across threshold and platform-type model families. \\

F3 & EUR 1.00 threshold in Local MaaS contexts. &
Very robust &
\coef{-0.229}{<0.001} &
\coef{-0.049}{0.002} &
Full sample, $N=14{,}514$; 90 Local MaaS high-fee observations. \\

F3 & EUR 1.00 threshold in multi-platform contexts. &
Very robust &
\coef{-0.146}{<0.001} &
\coef{-0.099}{<0.001} &
Full sample, $N=14{,}514$; 1,308 multi-platform high-fee observations. \\

F3 & EUR 1.20 threshold in Local MaaS contexts. &
Very robust &
\coef{-0.233}{<0.001} &
\coef{-0.047}{0.006} &
Full sample, $N=14{,}514$; 72 Local MaaS high-fee observations. \\

F3 & EUR 1.20 threshold in multi-platform contexts. &
Very robust &
\coef{-0.171}{<0.001} &
\coef{-0.082}{<0.001} &
Full sample, $N=14{,}514$; 1,029 multi-platform high-fee observations. \\

F3a & The Local MaaS high-fee penalty is not driven by one city. &
Robust &
Median city-drop estimate at EUR 1.00: -0.209 &
Median city-drop estimate at EUR 1.00: -0.035 &
All 13 leave-one-platform-city tests remain negative and significant for EUR 0.99, EUR 1.00, and EUR 1.20. \\

F3a & The multi-platform high-fee penalty is not a single-city artifact. &
Robust at EUR 1.00 and EUR 1.20 &
Median city-drop estimates: -0.107 at EUR 1.00 and -0.135 at EUR 1.20 &
Median city-drop estimates: -0.085 at EUR 1.00 and -0.073 at EUR 1.20 &
All 13 leave-one-platform-city tests remain negative and significant at the EUR 1.00 and EUR 1.20 thresholds. \\

F4a & Large aggregator-only membership does not show a stable high-fee penalty. &
Negative evidence &
\coef{-0.045}{0.066} &
\coef{-0.016}{0.325} &
Full sample, $N=14{,}514$. The high-fee effect is not a large-aggregator-only result. \\

F3b & The Local MaaS high-fee result generalises to trip activity. &
Robust for Local MaaS &
\coef{-1.014}{<0.001} &
\coef{-0.130}{<0.001} &
Full sample, $N=14{,}514$. The result is not merely a capacity-ratio artifact. \\

F3b & Multi-platform evidence is cleaner for utilisation than for trip activity. &
Moderate &
\coef{-0.538}{<0.001} &
\coef{-0.010}{0.873} &
Full sample, $N=14{,}514$. Strong in market models, not within unit. \\

F5 & Promotion in platform contexts is positive mainly within provider--city units. &
Moderate &
\coef{0.012}{0.424} &
\coef{0.0115}{<0.001} &
Full sample, $N=14{,}514$; 738 promotion observations. \\

F6 & Subscriber-free-minutes promotions fit multi-platform exposure. &
Exploratory mechanism evidence &
\coef{0.122}{<0.001} &
\coef{0.043}{<0.001} &
Full sample model, $N=14{,}514$, but treated support is only one city--provider cell with 144 observations. \\

F16 & Vehicle-type breadth buffers the Local MaaS high-fee penalty. &
Moderate to robust &
\coef{0.074}{<0.001} &
\coef{0.014}{<0.001} &
Full sample, $N=14{,}514$; 90 Local MaaS high-fee observations. \\

F19 & Relative same-mode unlock-fee disadvantage is harmful in Local MaaS contexts. &
Very robust; strongest new feature result &
\coef{-0.089}{<0.001} &
\coef{-0.030}{0.002} &
Full sample, $N=14{,}514$. The feature is available for the full panel. \\

F19 & Relative same-mode unlock-fee disadvantage is harmful in multi-platform contexts. &
Very robust &
\coef{-0.091}{<0.001} &
\coef{-0.041}{<0.001} &
Full sample, $N=14{,}514$. The feature is available for the full panel. \\

F20 & Relative per-minute price disadvantage is weaker than relative unlock-fee disadvantage. &
Moderate &
\coef{-0.104}{0.003} &
\coef{-0.020}{0.153} &
Full sample, $N=14{,}514$. Supports upfront-fee salience rather than generic price sensitivity. \\

F21 & Same-mode competition is a Local MaaS boundary condition. &
Moderate &
\coef{-0.059}{0.013} &
\coef{-0.019}{0.083} &
Full sample, $N=14{,}514$. Weaker than the relative unlock-fee gap. \\

F22 & Own same-mode availability helps in some platform contexts but does not offset high fees. &
Moderate &
\coef{-0.007}{0.819} for multi-platform &
\coef{0.019}{0.024} for multi-platform &
Full sample, $N=14{,}514$. Positive mainly within unit; high-fee triples remain problematic. \\

F23 & Local MaaS is less aligned with night-oriented usage. &
Moderate &
\coef{-0.019}{0.001} &
\coef{-0.018}{<0.001} &
Full sample, $N=14{,}514$. Usage-context evidence from observed trip timing. \\

F24 & Provider-level pass, free-unlock, reservation, and parking/geofence features are not robust estimators yet. &
Identification caveat &
Not interpreted because of collinearity &
Not interpreted because of weak within-unit variation &
The features are useful for theory and future coding, but current support is mostly provider-level. \\

F25 & Same-platform competitor count is not estimable cleanly. &
Not supported &
Implausibly large coefficients and missing p-values &
Unstable and collinear &
The measure is too mechanically tied to platform architecture and city/provider structure. \\

\end{longtable}
\normalsize

\section{Description of the Evidence}

The first empirical pattern is that platform membership is not a reliable main-effect
story. The market fixed-effect estimate is positive, but the effect disappears in the
stricter provider--city fixed-effect specification. This motivates the moderation logic:
platforms matter less as an independent treatment that raises utilisation everywhere and
more as an interface that changes how users evaluate the provider's marketing mix.

The second and most stable pattern is pricing friction. High upfront access fees are
consistently more harmful in platform contexts, especially in Local MaaS and multi-platform
settings. At the EUR 1.00 threshold, Local MaaS has a market fixed-effect coefficient of
-0.229 and a unit fixed-effect coefficient of -0.049. Multi-platform membership has a
market fixed-effect coefficient of -0.146 and a unit fixed-effect coefficient of -0.099.
The EUR 1.20 threshold produces the same qualitative conclusion.

The robustness checks strengthen this interpretation. The Local MaaS high-fee penalty
survives every leave-one-platform-city check at EUR 0.99, EUR 1.00, and EUR 1.20. The
multi-platform high-fee penalty survives every city-drop test at EUR 1.00 and EUR 1.20.
The Local MaaS result also appears in trip activity, which indicates that the finding is
not merely a mathematical artefact of the utilisation denominator.

The third pattern is that relative price position clarifies the mechanism. Providers with
higher unlock fees than their same-mode competitors perform worse in Local MaaS and
multi-platform contexts. The relative unlock-fee disadvantage is negative and significant
in both market and unit specifications. The analogous per-minute price disadvantage is
weaker. This distinction is central: platforms do not simply make all price differences
more important; they appear to make upfront access-price differences especially salient.

The fourth pattern is that other marketing-mix elements matter, but they are secondary.
Product breadth buffers the Local MaaS high-fee penalty, suggesting that a richer product
assortment can partially offset pricing friction by improving modal fit. Promotion shows
positive within-unit evidence, and subscriber-free-minutes promotions fit the multi-platform
logic, but the campaign evidence is localized. Same-mode competition is a useful boundary
condition, yet it is weaker than relative price position. Finally, provider-level pass,
reservation, and parking/geofence features are useful descriptive and theoretical variables,
but current variation is not sufficient for robust estimation.

\section{Interpretation and Narrative}

The results support a comparison-salience account of platform membership. Platforms change
the shopping and decision environment. They bring alternatives into the same interface,
make providers easier to compare, and increase the visibility of differences that might
otherwise be less salient. The central marketing consequence is that the same pricing
decision can have different effects inside and outside platform environments.

The strongest evidence concerns upfront access fees. Unlock fees are discrete, immediate,
and visible before the trip begins. They are therefore well suited to become salient in a
platform interface. Per-minute prices require users to anticipate trip duration and total
cost, which makes them less transparent at the point of choice. This explains why the
relative unlock-fee gap produces the strongest new feature result, while the relative
per-minute price gap is weaker.

Local MaaS and multi-platform contexts are the empirical core of the story. In these
contexts, users are not merely exposed to one additional booking channel. They are exposed
to a broader urban mobility choice architecture in which shared mobility competes with
other providers and, often, other transport modes. The platform therefore acts as a
comparison environment. A provider with a high or relatively high unlock fee becomes less
attractive precisely because the platform makes alternatives more visible.

The negative evidence for large aggregator-only membership is important. If the findings
were only a Free Now-style aggregator effect, the interpretation would be narrower and
less theoretically distinctive. Instead, the strongest evidence appears in local public
MaaS and multi-platform settings. This supports a broader claim about platform architecture:
the effect depends on how the platform structures choice, not merely on whether a provider
is present on a commercial aggregator.

The product-breadth result makes the narrative more balanced. Platform membership can
amplify pricing frictions, but providers are not powerless. Broader vehicle-type offerings
appear to buffer the Local MaaS high-fee penalty. This suggests an interaction between price
and product strategy: a salient access fee is harmful, but greater modal fit can soften the
effect. In marketing terms, platform participation raises the bar for internal consistency
across the mix. Price, product breadth, and availability need to work together.

The promotion findings point in a similar direction but remain empirically narrower.
Usage-cost reducing promotions such as subscriber free minutes fit the platform logic
because they counteract cost salience. However, the observed campaign support is too
localized for a central causal claim. The result should be framed as mechanism-consistent
evidence and as a priority for future city-date campaign coding.

Competition should be interpreted as an enabling condition rather than as the main
mechanism. Same-mode competition matters because it supplies alternatives that can be
compared. But the stronger result is not the competitor count itself; it is the provider's
relative access-price disadvantage. This means the paper should not argue simply that
competition moderates platform effects. A more precise claim is that platforms make
marketing-mix disadvantages more consequential when direct alternatives are available and
visible.

\section{Implications}

The empirical narrative can be stated as follows:

\begin{quote}
Platform membership reshapes marketing-mix effectiveness by changing the comparison
environment in which users evaluate mobility providers. In Local MaaS and multi-platform
contexts, high and relatively high unlock fees reduce capacity utilisation. The effect is
not a generic platform main effect, not a large aggregator-only result, and not driven by a
single city. Product breadth can buffer the penalty, while promotion and pass features
remain promising but require richer historical campaign coding.
\end{quote}

For the paper, the most defensible main results are: high unlock-fee thresholds in Local
MaaS and multi-platform contexts; relative same-mode unlock-fee disadvantage; leave-one-city
robustness; and trip-activity robustness for Local MaaS. Product breadth should be used as
a secondary moderation result. Promotion and provider-level pass/process features should
support the mechanism and motivate future data collection rather than anchor the main
identification claim.

\section{Limitations}

The analysis is observational and estimates conditional associations rather than randomized
treatment effects. Some platform architectures are structurally tied to specific cities and
providers, which is why unit fixed effects and leave-one-city checks are essential. Several
promising marketing-mix features, especially passes, reservations, and parking/geofence
rules, currently vary mostly at the provider level and therefore cannot be interpreted as
clean city-date effects. Promotion findings are based on limited campaign support. Same-
platform competitor counts are theoretically interesting but currently too collinear with
platform architecture to estimate cleanly.

\end{document}
